Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-03 draft.Rmd
Update draft.Rmd

## Mobility and theory

### Mobility and earnings:

@@

@@

The sample is drawn from the British Household Panel Survey, and the German Socio-Economic Panel, both are representative of British and German workers. Respondents in both panels are questioned annually, and the period studied covers 2000-2008. This period crosses both panels, and stops sampling workers before the European Debt Crisis. Since the crisis had significant negative effects in both rucailly countries, it is not representative of either labour market. Each panel contains socio-economic variables, detailed job history files, household composition details, employment details and several satisfaction measures.

@@

Estimation:

@@

Results:

@@

Hypotheses:

>>>>

## Micro-level theories on mobility

What are the micro-level theories on mobility and outcomes?

## Mobility and earnings:

@@

## Macro-level theories on mobility

@@

The sample is drawn from the British Household Panel Survey, and the German Socio-Economic Panel, both are representative of British and German workers. Respondents in both panels are questioned annually, and the period studied covers 2000-2008. This period crosses both panels, and stops sampling workers before the European Debt Crisis. Since the crisis had significant negative effects in both countries, it is not representative of either labour market, and so is ommitted. Each panel contains socio-economic variables, detailed job history files, household composition details, employment details and several satisfaction measures.

@@

## Estimation:

@@

## Results:

@@
